---
title: "F1 Data Analysis"
author: Aldrich Saladino
output: html_document
---

# Overview
Formula 1 is a sport heavily focused on the innovation and machine engineering, looking to push the boundaries of speed. This document will cover various different analysis and points of discussion, in a multipart series. The following topics are:
    * Lewis Hamilton vs Max Verstappen: Historical Comparisons
      * Mercedes AMG W11 vs Red Bull RB19 - 2 of F1's most dominant cars. Who's is faster in a head to head?
    * The influence of new car packages and upgrades. How much faster can upgrades be?
    * Mercedes Zero Side Pod Analysis - How and why did it go wrong?
    * Driver Statistics
      * Historically successul tracks per driver
        * Highest Placements, Lowest Placements
      * Stack Rankings/Power Rankings - based on data analysis
        * Historical average Placement
          * Rolling 3 year?
          * Avg speed 

## Installing Supporting Packages 
Once we are ready to ingest and manipulate the data in R, the correct packages must be installed. The following packages are used in the cleaning and processing for analysis using the following code:
  * tidyverse
  * ggplot2
  * dplyr
  * readr
  * janitor
  * skimr
  * scales
```{r load packages}
packages <- c("tidyverse", "ggplot2", "dplyr", "readr", "janitor", "skimr", "scales","purr")
for (package in packages) {
    if (!require(package, character.only = TRUE)) {
        install.packages(package)
    }
}
```

```{r import bulk csv list}
#Define a prefix path for the read
path_prefix <- "/Users/aldrichsaladino/Desktop/F1 Data/pre-work_and_csvs/"

#list these CSVs without the path prefix
csv_files <- c("status", "sprint_results", "seasons", "results", "races", "qualifying", "pit_stops", "lap_times", "drivers", "driver_standings", "constructors", "constructor_standings", "circuits")

# use the loop apply function to read through each of the CSV files and create a list of data frames for them
datasets <- lapply(csv_files, function(file) {
  readr::read_csv(paste0(path_prefix, file, ".csv"))
})

#set the names for each of the datsets in the list
names(datasets)  <- csv_files

# to access each dataset: datasets [["status"]] etc
```

```{r open all data}
datasets[["status"]]
```